data_cleaning_longer_period

### 2024-10-11 code/manuscript_altanalysis.Rmd
more analysis

@@

@@

df.temptemp <- df.mt %>% 
  rename(ID = ID.x) %>% 
  mutate(Closed = ifelse(lead(is.na(Sites)), 1, 0)) %>% 
  select(ClinicHHI, Att, `BHCMIS ID`, value, ID, MS, Year, Pct.NHA:Pct.Homeless, Qcomp, Total, Altman, logPatsPerStaff, 
         htn.rate, dm.rate, pap.rate, crc.rate, childbmi.rate, adultbmi.rate, Complexity, Intensity, Pct.MCD, Pct.MCR, Pct.COM, Pct.None, CostPerPat, quick_ratio, months_of_cash, Profitability, LiabPctAssets, Staff, Closed) %>% 
  unique()

  filter(value_min == value_max | value_last > value_first) %>% 
  mutate(value = ifelse(value >= 6, 6, value)) #%>% filter(Year < 2020)

@@

feols(I(Closed * 100) ~  Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | I((10000 - ClinicHHI)/1000) ~ Tx + factor(Year) + factor(ID) , cluster = "ID", data = df.temptemp)

@@

```{r}
 did2s(
      data = df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx))  , 
      yname = "ClinicHHI", 
      treatment = "Tx",
        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "ID",
      verbose = TRUE
    )

 event_study(data = df.temptemp ,
  yname = "ClinicHHI", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>%
  filter(abs(term) <= 6) %>%
  #filter(estimator == "Gardner (2021)") %>%
  filter(estimator == "Callaway and Sant'Anna (2020)") %>%
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ #theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) +
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("FirstStage: ") + xlab("Year Relative to Competitive Shock") + ylab("Percentage Points")

@@

df.z.temp <- df.z %>% mutate(Tx = ifelse(value - 1 > 1, 1, value - 1)) %>% filter(!is.na(Tx)) %>% mutate(DirectlyTreated = ifelse(Att.z > 2010, 1, 0)) %>% 
  filter(!(Att == 0 & DirectlyTreated == 1)) %>% 
        mutate(Pct.MCD = Medicaid / NumberofPatients * 100, 
               Pct.MCR = Medicare / NumberofPatients * 100, 
               Pct.COM = Private / NumberofPatients * 100,
               Pct.None = Uninsured / NumberofPatients * 100 ) %>% 
  select(NumberofPatients, Pct.MCD:Pct.None, Total.Hours, Sites, Mean.Hours, Perminance, Schedule, Calendar, Tx, DirectlyTreated, ID, Year, Zip, Att)

>>>>

```{r}
uds.covariates %>% 
  filter(`BHCMISID` == "010180")
```

@@

## More Cleaning
```{r}

df.temptemp <- df.mt %>% 
    rename(ID = ID.x) %>% 
    group_by(ID) %>% 
  mutate(Closed = ifelse(lead(is.na(Sites)), 100, 0)) %>% 
  select(ClinicHHI, Att, `BHCMIS ID`, value, ID, MS, Year, Pct.NHA:Pct.Homeless, Qcomp, Total, Altman, logPatsPerStaff, 
         htn.rate, dm.rate, pap.rate, crc.rate, childbmi.rate, adultbmi.rate, Complexity, Intensity, Pct.MCD, Pct.MCR, Pct.COM, Pct.None, CostPerPat, quick_ratio, months_of_cash, Profitability, LiabPctAssets, Staff, Closed) %>% 
  unique()

  filter(value_min == value_max | value_last > value_first) %>% 
  mutate(value = ifelse(value >= 6, 6, value)) #%>% group_by(ID) %>% mutate(max_Closures = max(Closed)) %>% filter(max_Closures == 0)

df.temptemp <- df.temptemp %>% 
  left_join (df.temptemp %>% 
  filter(value > value_min) %>% 
  group_by(ID) %>% 
  summarise(Att = min(Year)), by = c("ID")) %>% 
  mutate(Att = ifelse(!is.na(Att.y), Att.y, Att.x)) %>% 
  select(ClinicHHI, Att, `BHCMIS ID`, value, ID, MS, Year, Pct.NHA:Pct.Homeless, Qcomp, Total, Altman, logPatsPerStaff, 
         htn.rate, dm.rate, pap.rate, crc.rate, childbmi.rate, adultbmi.rate, Complexity, Intensity, Pct.MCD, Pct.MCR, Pct.COM, Pct.None, CostPerPat, quick_ratio, months_of_cash, Profitability, LiabPctAssets, Staff, Closed:Tx) %>% 
  unique()

@@

@@

model <- feols(Complexity ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless   | I((10000 - ClinicHHI)/1000) ~ Tx  + factor(Year) + factor(ID), cluster = "ID", data = df.temptemp)
summary(model)

model <- lm(data = df.temptemp, Pct.None ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless   + Tx + factor(Year) + factor(ID) )
summary(model)

@@

```{r}
 did2s(
      data = df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)  )   , 
      yname = "Complexity", 
      treatment = "Tx",
        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "ID",
      verbose = TRUE
    )

 event_study(data = df.temptemp ,
  yname = "ClinicHHI", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>%
  filter(abs(term) <= 6) %>%
  #filter(estimator == "Gardner (2021)") %>%
  #filter(estimator == "Callaway and Sant'Anna (2020)") %>%
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ #theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) +
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("FirstStage: ") + xlab("Year Relative to Competitive Shock") + ylab("Percentage Points")

## Alt DID estimates

coeffs.did <- c(0,0,0,0)

  df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx))
  colnames(df.temptemptemp)[(16+k)] <- "Outcome"
  model <-  did2s(
      data = df.temptemptemp, 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "ID",
      verbose = TRUE
    )

  coeffs.did <- rbind(coeffs.did, model$coeftable[1,])

core.did.estimates <- data.frame(cbind(colnames(df.temptemp)[17:38], (coeffs.did[-1,]))) %>% 
  #select(V1, Estimate, Pr...t.., Estimate.1, Pr...t...1) %>% 
  mutate(Estimate = round(as.numeric(Estimate), 2), `95% CI` = paste(round(as.numeric(Estimate) - 1.96 * as.numeric(`Std..Error`), 2), ", ", round(as.numeric(Estimate) + 1.96 * as.numeric(`Std..Error`), 2), sep = "")) %>% 
  select(V1, Estimate, `95% CI`)

core.did.estimates <- core.did.estimates
rownames(core.did.estimates) <- NULL

core.did.estimates %>% 
  kable("html", booktabs = T, col.names = c("Outcome","Estimate","95% CI")) %>% 
  kable_styling(latex_options = c("striped")) %>%
  pack_rows(index = c("Overall Impacts" = 4, "Quality of Care" = 6, "Patient Complexity" = 2, "Payer Mix" = 4, "Finances" = 6)) %>% 
  add_header_above(c("IV-Estimated LATE Effects of Competitive Shocks on Incumbent Clinics" = 3))

@@

df.z.temp <- df.z %>% mutate(Tx = ifelse(value - 1 > 1, 1, value - 1)) %>% filter(!is.na(Tx)) %>% mutate(DirectlyTreated = ifelse(Att.z > 2010, 1, 0)) %>% 
  filter(!(Att == 0 & DirectlyTreated == 1)) %>% 
        mutate(Pct.MCD = Medicaid / NumberofPatients * 100, 
               Pct.MCR = Medicare / NumberofPatients * 100, 
               Pct.COM = Private / NumberofPatients * 100,
               Pct.None = Uninsured / NumberofPatients * 100 ) %>% 
  select(NumberofPatients, Pct.MCD:Pct.None, Total.Hours, Sites, Mean.Hours, Perminance, Schedule, Calendar, Tx, DirectlyTreated, ID, Year, Zip, Att, `BHCMIS ID`)

### 2024-10-11 code/manuscript_data_cleaning.Rmd
more analysis

uds.covariates %>% 
  arrange(BHCMISID, Year)

@@

>>>>

uds.covariates %>% 
  arrange(BHCMISID, Year)
uds.covariates %>% 
  filter(Pct.Homeless > 99)

@@

## Add updated data
ufins.revenue.expenses <- read.csv("//Users/markow/Dropbox/Git/Data/Updated_FQHC_Revenue_vs_Expenses.csv", header = TRUE)
table(ufins.revenue.expenses$X.form_year..)
names(ufins.revenue.expenses) <- gsub("^X\\.", "", names(ufins.revenue.expenses))
names(ufins.revenue.expenses) <- gsub("\\.\\.", "", names(ufins.revenue.expenses))

ustaffing <- read.csv("/Users/markow/Dropbox/Git/Data/Updated_FQHC_Staffing.csv")
uassliabs <- read.csv("/Users/markow/Dropbox/Git/Data/Updated_FQHC_Assets_and_Liabilities.csv")

ufins <- uds.cw %>% filter(Year == 2011) %>% unique() %>% select(ModernGranteeID, BHCMIS.ID) %>% 
  left_join(cw, by = c("ModernGranteeID" = "Grant Number")) %>% 
  left_join(ufins.revenue.expenses, by = c("EIN" = "EIN")) %>% 
  select(ModernGranteeID:EIN, form_year:fringe_rate) %>% 
  left_join(ustaffing %>% select(EIN:Staff), by = c("EIN","form_year" = "Year")) %>% 
  left_join(uassliabs %>% select(EIN:Liabilities), by = c("EIN","form_year" = "Year"))

fins.revenue.expenses <- ufins
